Stay in shape! Homework exam II

### 2016-04-03 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
query time

Now we have the outer tree that is a binary tree based on $y$ coordinates.
For each interval node $v$ we have a canoconical subset $S_v \subseteq S$
of all linesegments that appear in the subtree rooted at node $v$.
Note that $subtree(c_{left}(v))\cup subtree(c_{right}(v)) = subtree(v)$
where $subtree$ is a function that returns the subtree of $v$ and 
$c_{right}$ returns the right child and $c_{left}$ returns the left child.
Every level of the outer tree has an $n$ amount of items stored in its
subtrees. Because at deeper level the subtrees get split further.
This results in the following order of storage:

@@

@@

\section{Voronoi nearest neigbour\emph{s}}
%TODO: wtf? maybe with higher order voronoi?? But it won't be log n
%TODO: we hebben ook bogen. Kun je representateren als een lijn en een punt.

>>>>

Now we have the outer tree that is a binary tree based on $y$ coordinates.
For each interval node $v$ we have a canoconical subset $S_v \subseteq S$
of all linesegments that appear in the subtree rooted at node $v$.
Note that $subtree(c_{left}(v))\cup subtree(c_{right}(v)) = subtree(v)$
where $subtree$ is a function that returns the subtree of $v$ and 
$c_{right}$ returns the right child and $c_{left}$ returns the left child.
Every level of the outer tree has an $n$ amount of items stored in its
subtrees, and there are $log(n)$ levels because no 2 line segments have the
same y coordinate. This results in the following order of storage:

@@

The result also will not contain any duplicates, because
when someting is repoted to the right in the main tree
the algorithm will go to the left, so the next tree only
contains things that weren't in the original report.

@@

When we traverse the tree we spend at most $O(1+r_v)$ time at
that node $v$ where $r_v$ is the time spend reporting the results.
Summing over all $r_v$ results in $r$. The depth of the main tree
is $log(n)$. we visit at most two nodes at any depth of the tree.
This results in:

\[ 2\cdot (log(n)+r)\]

time to traverse it. Now we will fill in R by analysing the
inner tree. At any node $v$ we visit we spend $O(1+k_v)$ time where
$k_v$ is the number of linesegments we report at $v$. Summing
over $k_v$ results in $k$. The depth of the tree is $log(n)$,
we visit at most one node at any depth of the tree. This results in:

\[ log(n)+k\]

So now we can fill in $r$:

\[ 2\cdot (log(n)+log(n)+k)\]

Which results in:

\[ O(log(n)+k) \]

query time.
\section{Voronoi nearest neigbour\emph{s}}
\subsection{Storage}
\subsection{Query time}
%TODO: wtf? maybe with higher order voronoi?? But it won't be log n
%TODO: we hebben ook bogen. Kun je representateren als een lijn en een punt.
